\documentclass[11]{article}
\usepackage[utf8]{inputenc}
\usepackage{float}
\usepackage[pdfstartview=FitH, CJKbookmarks=true, bookmarksnumbered=true,
            bookmarksopen=true,
            colorlinks, pdfborder=001, linkcolor=red, anchorcolor=blue, citecolor=blue]{hyperref}
\usepackage{ragged2e, amsmath,  array, amsfonts}
\usepackage{tcolorbox, color}
\usepackage{caption, subcaption, graphicx}
\usepackage{geometry}

\newgeometry{hmargin={1.3in, 1.3in}}   % set the margins
%\newgeometry{vmargin={1mm}, hmargin={12mm,17mm}}   % set the margins



\tcbuselibrary{theorems}

\newtcbtheorem[number within=section]{mytheo}{  }%
{colback=white!5,colframe=red!50!black,fonttitle=\bfseries}{th}

\title{Test-plan \\ \large{Value-based  recommendation}}
%\author{Aditya Kiran }
\date{}


\input{./ak-preamble.tex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document} %JSR
\maketitle


\section{Formulation}

\vspace{0.3cm}

\redak{\sdhd{Problem Statement:}}\\
Now, the problem statement is: \\
Given that a user is reading an article $A_i$, what article must be recommended next so that we
\begin{enumerate}
\item maximize the content relevance to the user
\item maximize the ad-monetary value.
\end{enumerate} 

Mathematically, given $A_i$, we seek $A_j$ such that:
\begin{align*}
 j&= \argmax_J   \phi(A_i, A_{J}) ,
\end{align*}
where $\phi$ is the utility function. This above formulation is mainly for our \textit{Read Next} pages, but it could be easily extended to \textit{Infinite scroll}.

\section{Testing}

\redak{\sdhd{What questions do we intend to answer via the  test}}\\
\begin{enumerate}
\item How much monetary lift do we observe? 
\item How is the AQ degrading?
\end{enumerate}



\textbf{Some notation:}
\begin{itemize}
\item \textit{val} is the test-side and \textit{bau} is the control side
\item Let $\{ A_1, A_2, \cdots A_N \}$ be the $N$ articles that were served as a part of showing 3 recommendation for each of the 500 test head-articles.
\item Let $R_i^{val}$ and $R_i^{bau}$ be the total revenue obtained on the $A_i^{th}$ article throughout the testing period.
\item Let $I_i^{val}$ and $I_i^{bau}$ be the total impressions obtained on the $A_i^{th}$ article throughout the testing period.
\item Let $V_i^{val}$ and $V_i^{bau}$ be the total page-views observed on the $A_i^{th}$ article throughout the testing period.
\item Let $S_i^{val}$ and $S_i^{bau}$ be the total sessions on the $A_i^{th}$ article throughout the testing period.
\end{itemize}


\subsection{Lift in the monetary value}
So the metrics that we are interested in this regard:
\begin{enumerate}

\item Percentage lift in the `value ' or the revenue per impression:

\begin{enumerate}
\item Lift in the `value' evaluated over all the $N$ articles:
\[    \dfrac{\left(  \frac{\sum_i R_i^{val}}{\sum_i I_i^{val}} - \frac{\sum_i R_i^{bau}}{\sum_i I_i^{bau}} \right)}{ \left( \frac{\sum_i R_i^{bau}}{\sum_i I_i^{bau}} \right) } \times 100   \]
\item Mean of the lifts observed across each of the $N$ articles:
\[     \frac{1}{N} \sum_i   \dfrac{  \left(  \frac{R^{val}_i}{I^{val}_i}  - \frac{R^{bau}_i}{I^{bau}_i}  \right)  }{\left( \frac{R^{bau}_i}{I^{bau}_i} \right)}      \]
This is more sensitive if we are dealing with high-rev pages but with few impressions
\end{enumerate}



\item Percentage lift in the revenue 
\[    \dfrac{\left( \sum_i R_i^{val}- \sum_i R_i^{bau} \right)}{\sum_i R_i^{bau}} \times 100   \]
Although, this wouldn't make much sense if the no. of impressions is widely different in bau and val.
\end{enumerate}

\subsection{Degradation in the audience quality}
Currently the AQ metrics that the business has in mind are off-limits for us, as they are only measured through an aggregate of full month of a specific program. So we need to look at some other pseudo-metrics that measure AQ.

So we intend to look at user engagement via PVPS.

\begin{enumerate}

\item  Reduction in the PVPS:
\[  -  \dfrac{\left(  \frac{\sum_i V_i^{val}}{\sum_i S_i^{val}} - \frac{\sum_i V_i^{bau}}{\sum_i S_i^{bau}} \right)}{ \left( \frac{\sum_i V_i^{bau}}{\sum_i S_i^{bau}} \right) } \times 100   \]
\item We could do similar comparisions using other metrics too such as 

\begin{itemize}
\item ASD
\item bounce-rate
\item IAB ad CTR
\end{itemize}

\end{enumerate}

\section{Conclusion}
Finally we want to test our hypothesis that serving high-value pages (obtained by optimizing our utility function $\phi$ over all the available articles) is not detrimental to the AQ or the user-engagement.




\end{document}
